R Notebook

### 2022-04-19 R/HumanDeaminationAnalysis.rmd
Update HumanDeaminationAnalysis.rmd

# Read in the relevant data
CPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
CPDMismatchDataFilePaths$rep1 = list(
  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_mismatches.bed"),
  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_mismatches.bed"),
  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_mismatches.bed"),
  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_mismatches.bed")
)
CPDMismatchDataFilePaths$rep2 = list(
  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_mismatches.bed"),
  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_mismatches.bed"),
  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_mismatches.bed"),
  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_mismatches.bed")
)

sixFourMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
sixFourMismatchDataFilePaths$rep1 = list(
  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_mismatches.bed"),
  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_mismatches.bed"),
  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_mismatches.bed")
)
sixFourMismatchDataFilePaths$rep2 = list(
  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_mismatches.bed"),
  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_mismatches.bed"),
  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_mismatches.bed")
)

@@

@@

```{r acquire_and_format_data_2}
load(file.path(deaminationDataDirectory, "NHF1_deamination_periodicity_results.rda"))
dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))

@@

>>>>

# Read in the relevant data
CPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
CPDMismatchDataFilePaths$rep1 = list(
  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_mismatches_by_read.bed"),
  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_mismatches_by_read.bed"),
  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_mismatches_by_read.bed"),
  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_mismatches_by_read.bed")
)
CPDMismatchDataFilePaths$rep2 = list(
  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_mismatches_by_read.bed"),
  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_mismatches_by_read.bed"),
  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_mismatches_by_read.bed"),
  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_mismatches_by_read.bed")
)

sixFourMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
sixFourMismatchDataFilePaths$rep1 = list(
  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_mismatches_by_read.bed"),
  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_mismatches_by_read.bed"),
  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_mismatches_by_read.bed")
)
sixFourMismatchDataFilePaths$rep2 = list(
  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_mismatches_by_read.bed"),
  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_mismatches_by_read.bed"),
  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_mismatches_by_read.bed")
)

@@

# Get the tables of read length vs. GC content
CPDReadLengthVsGCData = lapply(CPDMismatchData, function(x) lapply(
  x, getReadLengthAndGCContent
))
sixReadLengthVsGCData = lapply(sixFourMismatchData, function(x) lapply(
  x, getReadLengthAndGCContent
))

@@

```{r read_length_vs_GC_content}

@@

```{r acquire_and_format_data_2}
load(file.path(deaminationDataDirectory, "NHF1_deamination_periodicity_results.rda"))
dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
```
